Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-18 SupportingInformation.Rmd
adding chunk for C, SC : ar1 results with beta = 0.5, -0.5

```{r cause4copula_stat_clayton_ar1_posbeta, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
#source("Cause4copula.R")
#-----------------
#set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model 
#resloc<-"./Results/Cause4copula_results/"
#model<-"ar1"
#params<-c(0.5) # this parameter is beta in ar1 model
#tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,sep="")

#if (!dir.exists(tempo)){
#  dir.create(tempo)
#}

#resloc<-paste(tempo,"/",sep="")

# for clayton with spearman and kendall method
#Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
#                          params=params,p0=c(0,0),model="ar1")

#Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
#                          params=params,p0=c(0,0),model="ar1")

# for survival clayton with spearman and kendall method
#Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
#                          params=params,p0=c(0,0),model="ar1")

#Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
#                          params=params,p0=c(0,0),model="ar1")
```

```{r cause4copula_stat_clayton_ar1_negbeta, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model 
resloc<-"./Results/Cause4copula_results/"
model<-"ar1"
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,sep="")

@@

resloc<-paste(tempo,"/",sep="")

# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")               
```

>>>>

```{r cause4copula_stat_ar1_clayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model 
resloc<-"./Results/Cause4copula_results/"
model<-"ar1"
params<-c(0.5) # this parameter is beta in ar1 model
fcode<-3

tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")

@@

resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")
```

```{r cause4copula_stat_ar1_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model 
resloc<-"./Results/Cause4copula_results/"
model<-"ar1"
params<-c(0.5) # this parameter is beta in ar1 model
fcode<-13

tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,"_",BiCopName(fcode,short=F),sep="")

resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")
```
